Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-07-21 paper/submission/paper.tex
submitted version

\graphicspath{{figures/}{figures/violin_scattering/}{figures/flute_scattering/}{./}}
%%% Put your definitions there:
\startlocaldefs

@@

\bibliographystyle{bmc-mathphys}
\bibliography{bib}

>>>>

\graphicspath{{figures/}{figures/violin_scattering}{figures/flute_scattering}{./}}
%%% Put your definitions there:
\startlocaldefs

@@

% \bibliographystyle{bmc-mathphys}
% \bibliography{bib}

%% BioMed_Central_Bib_Style_v1.01

\begin{thebibliography}{78}
% BibTex style file: bmc-mathphys.bst (version 2.1), 2014-07-24
\ifx \bisbn   \undefined \def \bisbn  #1{ISBN #1}\fi
\ifx \binits  \undefined \def \binits#1{#1}\fi
\ifx \bauthor  \undefined \def \bauthor#1{#1}\fi
\ifx \batitle  \undefined \def \batitle#1{#1}\fi
\ifx \bjtitle  \undefined \def \bjtitle#1{#1}\fi
\ifx \bvolume  \undefined \def \bvolume#1{\textbf{#1}}\fi
\ifx \byear  \undefined \def \byear#1{#1}\fi
\ifx \bissue  \undefined \def \bissue#1{#1}\fi
\ifx \bfpage  \undefined \def \bfpage#1{#1}\fi
\ifx \blpage  \undefined \def \blpage #1{#1}\fi
\ifx \burl  \undefined \def \burl#1{\textsf{#1}}\fi
\ifx \doiurl  \undefined \def \doiurl#1{\textsf{#1}}\fi
\ifx \betal  \undefined \def \betal{\textit{et al.}}\fi
\ifx \binstitute  \undefined \def \binstitute#1{#1}\fi
\ifx \binstitutionaled  \undefined \def \binstitutionaled#1{#1}\fi
\ifx \bctitle  \undefined \def \bctitle#1{#1}\fi
\ifx \beditor  \undefined \def \beditor#1{#1}\fi
\ifx \bpublisher  \undefined \def \bpublisher#1{#1}\fi
\ifx \bbtitle  \undefined \def \bbtitle#1{#1}\fi
\ifx \bedition  \undefined \def \bedition#1{#1}\fi
\ifx \bseriesno  \undefined \def \bseriesno#1{#1}\fi
\ifx \blocation  \undefined \def \blocation#1{#1}\fi
\ifx \bsertitle  \undefined \def \bsertitle#1{#1}\fi
\ifx \bsnm \undefined \def \bsnm#1{#1}\fi
\ifx \bsuffix \undefined \def \bsuffix#1{#1}\fi
\ifx \bparticle \undefined \def \bparticle#1{#1}\fi
\ifx \barticle \undefined \def \barticle#1{#1}\fi
\ifx \bconfdate \undefined \def \bconfdate #1{#1}\fi
\ifx \botherref \undefined \def \botherref #1{#1}\fi
\ifx \url \undefined \def \url#1{\textsf{#1}}\fi
\ifx \bchapter \undefined \def \bchapter#1{#1}\fi
\ifx \bbook \undefined \def \bbook#1{#1}\fi
\ifx \bcomment \undefined \def \bcomment#1{#1}\fi
\ifx \oauthor \undefined \def \oauthor#1{#1}\fi
\ifx \citeauthoryear \undefined \def \citeauthoryear#1{#1}\fi
\ifx \endbibitem  \undefined \def \endbibitem {}\fi
\ifx \bconflocation  \undefined \def \bconflocation#1{#1}\fi
\ifx \arxivurl  \undefined \def \arxivurl#1{\textsf{#1}}\fi
\csname PreBibitemsHook\endcsname

%%% 1
\bibitem{downie2003mir}
\begin{barticle}
\bauthor{\bsnm{Downie}, \binits{J.S.}}:
\batitle{Music information retrieval}.
\bjtitle{Annual review of information science and technology}
\bvolume{37}(\bissue{1}),
\bfpage{295}--\blpage{340}
(\byear{2003})
\end{barticle}
\endbibitem

%%% 2
\bibitem{siedenburg2019chapter}
\begin{bbook}
\bauthor{\bsnm{Siedenburg}, \binits{K.}},
\bauthor{\bsnm{Saitis}, \binits{C.}},
\bauthor{\bsnm{McAdams}, \binits{S.}}:
In: \beditor{\bsnm{Siedenburg}, \binits{K.}},
\beditor{\bsnm{Saitis}, \binits{C.}},
\beditor{\bsnm{McAdams}, \binits{S.}},
\beditor{\bsnm{Popper}, \binits{A.N.}},
\beditor{\bsnm{Fay}, \binits{R.R.}} (eds.)
\bbtitle{The Present, Past, and Future of Timbre Research},
pp. \bfpage{1}--\blpage{19}.
\bpublisher{Springer},
\blocation{Cham}
(\byear{2019})
\end{bbook}
\endbibitem

%%% 3
\bibitem{faure1996icmpc}
\begin{bchapter}
\bauthor{\bsnm{Faure}, \binits{A.}},
\bauthor{\bsnm{McAdams}, \binits{S.}},
\bauthor{\bsnm{Nosulenko}, \binits{V.}}:
\bctitle{Verbal correlates of perceptual dimensions of timbre}.
In: \bbtitle{Proceedings of the International Conference on Music Perception
  and Cognition (ICMPC)}
(\byear{1996})
\end{bchapter}
\endbibitem

%%% 4
\bibitem{lostanlen2018extended}
\begin{bchapter}
\bauthor{\bsnm{Lostanlen}, \binits{V.}},
\bauthor{\bsnm{And{\'e}n}, \binits{J.}},
\bauthor{\bsnm{Lagrange}, \binits{M.}}:
\bctitle{Extended playing techniques: the next milestone in musical instrument
  recognition}.
In: \bbtitle{Proceedings of the International Conference on Digital Libraries
  for Musicology (DLfM)},
pp. \bfpage{1}--\blpage{10}
(\byear{2018}).
\bcomment{ACM}
\end{bchapter}
\endbibitem

%%% 5
\bibitem{antoine2018isma}
\begin{bchapter}
\bauthor{\bsnm{Antoine}, \binits{A.}},
\bauthor{\bsnm{Miranda}, \binits{E.R.}}:
\bctitle{Musical acoustics, timbre, and computer-aided orchestration
  challenges}.
In: \bbtitle{Proc. ISMA}
(\byear{2018})
\end{bchapter}
\endbibitem

%%% 6
\bibitem{kolozali2011ismir}
\begin{bchapter}
\bauthor{\bsnm{Kolozali}, \binits{S.}},
\bauthor{\bsnm{Barthet}, \binits{M.}},
\bauthor{\bsnm{Fazekas}, \binits{G.}},
\bauthor{\bsnm{Sandler}, \binits{M.B.}}:
\bctitle{Knowledge representation issues in musical instrument ontology
  design.}
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2011})
\end{bchapter}
\endbibitem

%%% 7
\bibitem{calvo2020acm}
\begin{botherref}
\oauthor{\bsnm{Calvo-Zaragoza}, \binits{J.}},
\oauthor{\bsnm{Haji\v{c}~Jr.}, \binits{J.}},
\oauthor{\bsnm{Pacha}, \binits{A.}}:
Understanding optical music recognition.
ACM Computing Surveys
(2020)
\end{botherref}
\endbibitem

%%% 8
\bibitem{erickson1975book}
\begin{bbook}
\bauthor{\bsnm{Erickson}, \binits{R.}}:
\bbtitle{Sound Structure in Music}.
\bpublisher{University of California Press}, \blocation{???}
(\byear{1975})
\end{bbook}
\endbibitem

%%% 9
\bibitem{thoret2018jasa}
\begin{barticle}
\bauthor{\bsnm{Thoret}, \binits{E.}},
\bauthor{\bsnm{Caramiaux}, \binits{B.}},
\bauthor{\bsnm{Depalle}, \binits{P.}},
\bauthor{\bsnm{McAdams}, \binits{S.}}:
\batitle{Human dissimilarity ratings of musical instrument timbre: A
  computational meta-analysis}.
\bjtitle{Journal of the Acoustical Society of America}
\bvolume{143}(\bissue{3}),
\bfpage{1745}--\blpage{1746}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 10
\bibitem{maresz2013cmr}
\begin{barticle}
\bauthor{\bsnm{Maresz}, \binits{Y.}}:
\batitle{On computer-assisted orchestration}.
\bjtitle{Contemporary Music Review}
\bvolume{32}(\bissue{1}),
\bfpage{99}--\blpage{109}
(\byear{2013})
\end{barticle}
\endbibitem

%%% 11
\bibitem{caetano2019swarm}
\begin{barticle}
\bauthor{\bsnm{Caetano}, \binits{M.}},
\bauthor{\bsnm{Zacharakis}, \binits{A.}},
\bauthor{\bsnm{Barbancho}, \binits{I.}},
\bauthor{\bsnm{Tard{\'o}n}, \binits{L.J.}}:
\batitle{Leveraging diversity in computer-aided musical orchestration with an
  artificial immune system for multi-modal optimization}.
\bjtitle{Swarm and Evolutionary Computation}
\bvolume{50},
\bfpage{100484}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 12
\bibitem{anden2015mlsp}
\begin{bchapter}
\bauthor{\bsnm{And{\'e}n}, \binits{J.}},
\bauthor{\bsnm{Lostanlen}, \binits{V.}},
\bauthor{\bsnm{Mallat}, \binits{S.}}:
\bctitle{Joint time-frequency scattering for audio classification}.
In: \bbtitle{Proceedings of the IEEE International Workshop on Machine Learning
  for Signal Processing (MLSP)},
pp. \bfpage{1}--\blpage{6}
(\byear{2015}).
\bcomment{IEEE}
\end{bchapter}
\endbibitem

%%% 13
\bibitem{anden2019tsp}
\begin{barticle}
\bauthor{\bsnm{And\'{e}n}, \binits{J.}},
\bauthor{\bsnm{Lostanlen}, \binits{V.}},
\bauthor{\bsnm{Mallat}, \binits{S.}}:
\batitle{Joint time--frequency scattering}.
\bjtitle{IEEE Transactions on Signal Processing}
\bvolume{67}(\bissue{14}),
\bfpage{3704}--\blpage{3718}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 14
\bibitem{lostanlen2018jasmp}
\begin{barticle}
\bauthor{\bsnm{Lostanlen}, \binits{V.}},
\bauthor{\bsnm{Lafay}, \binits{G.}},
\bauthor{\bsnm{And{\'e}n}, \binits{J.}},
\bauthor{\bsnm{Lagrange}, \binits{M.}}:
\batitle{Relevance-based quantization of scattering features for unsupervised
  mining of environmental audio}.
\bjtitle{EURASIP Journal on Audio, Speech, and Music Processing}
\bvolume{2018}(\bissue{1}),
\bfpage{15}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 15
\bibitem{anden2012scattering}
\begin{bchapter}
\bauthor{\bsnm{And\'{e}n}, \binits{J.}},
\bauthor{\bsnm{Mallat}, \binits{S.}}:
\bctitle{Scattering representation of modulated sounds}.
In: \bbtitle{Proceedings of the International Conference on Digital Audio
  Effects (DAFx)}
(\byear{2012})
\end{bchapter}
\endbibitem

%%% 16
\bibitem{weinberger2009distance}
\begin{barticle}
\bauthor{\bsnm{Weinberger}, \binits{K.Q.}},
\bauthor{\bsnm{Saul}, \binits{L.K.}}:
\batitle{Distance metric learning for large margin nearest neighbor
  classification}.
\bjtitle{Journal of Machine Learning Research}
\bvolume{10}(\bissue{Feb}),
\bfpage{207}--\blpage{244}
(\byear{2009})
\end{barticle}
\endbibitem

%%% 17
\bibitem{mcadams1995psychres}
\begin{barticle}
\bauthor{\bsnm{McAdams}, \binits{S.}},
\bauthor{\bsnm{Winsberg}, \binits{S.}},
\bauthor{\bsnm{Donnadieu}, \binits{S.}},
\bauthor{\bsnm{De~Soete}, \binits{G.}},
\bauthor{\bsnm{Krimphoff}, \binits{J.}}:
\batitle{Perceptual scaling of synthesized musical timbres: common dimensions,
  specificities, and latent subject classes}.
\bjtitle{Psychological research}
\bvolume{58}(\bissue{3}),
\bfpage{177}--\blpage{192}
(\byear{1995})
\end{barticle}
\endbibitem

%%% 18
\bibitem{patil2012ploscompbiol}
\begin{barticle}
\bauthor{\bsnm{Patil}, \binits{K.}},
\bauthor{\bsnm{Pressnitzer}, \binits{D.}},
\bauthor{\bsnm{Shamma}, \binits{S.}},
\bauthor{\bsnm{Elhilali}, \binits{M.}}:
\batitle{Music in our ears: {The} biological bases of musical timbre
  perception}.
\bjtitle{PLoS Computational Biology}
\bvolume{8}(\bissue{11}),
\bfpage{1002759}
(\byear{2012})
\end{barticle}
\endbibitem

%%% 19
\bibitem{joder2009taslp}
\begin{barticle}
\bauthor{\bsnm{Joder}, \binits{C.}},
\bauthor{\bsnm{Essid}, \binits{S.}},
\bauthor{\bsnm{Richard}, \binits{G.}}:
\batitle{Temporal integration for audio classification with application to
  musical instrument classification}.
\bjtitle{IEEE Transactions on Audio, Speech, and Language Processing}
\bvolume{17}(\bissue{1}),
\bfpage{174}--\blpage{186}
(\byear{2009})
\end{barticle}
\endbibitem

%%% 20
\bibitem{siedenburg2016jnmr}
\begin{barticle}
\bauthor{\bsnm{Siedenburg}, \binits{K.}},
\bauthor{\bsnm{Fujinaga}, \binits{I.}},
\bauthor{\bsnm{McAdams}, \binits{S.}}:
\batitle{A comparison of approaches to timbre descriptors in music information
  retrieval and music psychology}.
\bjtitle{Journal of New Music Research}
\bvolume{45}(\bissue{1}),
\bfpage{27}--\blpage{41}
(\byear{2016})
\end{barticle}
\endbibitem

%%% 21
\bibitem{martin1998asa}
\begin{bchapter}
\bauthor{\bsnm{Martin}, \binits{K.D.}},
\bauthor{\bsnm{Kim}, \binits{Y.E.}}:
\bctitle{Musical instrument identification: A pattern recognition approach}.
In: \bbtitle{Proceedings of the Acoustical Society of America}
(\byear{1998})
\end{bchapter}
\endbibitem

%%% 22
\bibitem{brown1999jasa}
\begin{barticle}
\bauthor{\bsnm{Brown}, \binits{J.C.}}:
\batitle{Computer identification of musical instruments using pattern
  recognition with cepstral coefficients as features}.
\bjtitle{The Journal of the Acoustical Society of America}
\bvolume{105}(\bissue{3}),
\bfpage{1933}--\blpage{1941}
(\byear{1999})
\end{barticle}
\endbibitem

%%% 23
\bibitem{eronen2000icassp}
\begin{bchapter}
\bauthor{\bsnm{Eronen}, \binits{A.}},
\bauthor{\bsnm{Klapuri}, \binits{A.}}:
\bctitle{Musical instrument recognition using cepstral coefficients and
  temporal features}.
In: \bbtitle{Proceedings of the IEEE International Conference on Acoustics,
  Speech, and Signal Processing (ICASSP)}
(\byear{2000})
\end{bchapter}
\endbibitem

%%% 24
\bibitem{herrera2003jnmr}
\begin{barticle}
\bauthor{\bsnm{Herrera~Boyer}, \binits{P.}},
\bauthor{\bsnm{Peeters}, \binits{G.}},
\bauthor{\bsnm{Dubnov}, \binits{S.}}:
\batitle{Automatic classification of musical instrument sounds}.
\bjtitle{Journal of New Music Research}
\bvolume{32}(\bissue{1}),
\bfpage{3}--\blpage{21}
(\byear{2003})
\end{barticle}
\endbibitem

%%% 25
\bibitem{wieczorkowska2003jiis}
\begin{barticle}
\bauthor{\bsnm{Wieczorkowska}, \binits{A.A.}},
\bauthor{\bsnm{{\.Z}ytkow}, \binits{J.M.}}:
\batitle{Analysis of feature dependencies in sound description}.
\bjtitle{Journal of Intelligent Information Systems}
\bvolume{20}(\bissue{3}),
\bfpage{285}--\blpage{302}
(\byear{2003})
\end{barticle}
\endbibitem

%%% 26
\bibitem{livshin2004dafx}
\begin{bchapter}
\bauthor{\bsnm{Livshin}, \binits{A.}},
\bauthor{\bsnm{Rodet}, \binits{X.}}:
\bctitle{Musical instrument identification in continuous recordings}.
In: \bbtitle{Proceedings of the International Conference on Digital Audio
  Effects (DAFx)}
(\byear{2004})
\end{bchapter}
\endbibitem

%%% 27
\bibitem{krishna2004icassp}
\begin{bchapter}
\bauthor{\bsnm{Krishna}, \binits{A.G.}},
\bauthor{\bsnm{Sreenivas}, \binits{T.V.}}:
\bctitle{Music instrument recognition: from isolated notes to solo phrases}.
In: \bbtitle{Proceedings of the IEEE International Conference on Acoustics,
  Speech, and Signal Processing (ICASSP)}
(\byear{2004})
\end{bchapter}
\endbibitem

%%% 28
\bibitem{kaminskyj2005jiis}
\begin{barticle}
\bauthor{\bsnm{Kaminskyj}, \binits{I.}},
\bauthor{\bsnm{Czaszejko}, \binits{T.}}:
\batitle{{Automatic recognition of isolated monophonic musical instrument
  sounds using kNNC}}.
\bjtitle{Journal of Intelligent Information Systems}
\bvolume{24}(\bissue{2-3}),
\bfpage{199}--\blpage{221}
(\byear{2005})
\end{barticle}
\endbibitem

%%% 29
\bibitem{benetos2006icassp}
\begin{bchapter}
\bauthor{\bsnm{Benetos}, \binits{E.}},
\bauthor{\bsnm{Kotti}, \binits{M.}},
\bauthor{\bsnm{Kotropoulos}, \binits{C.}}:
\bctitle{Musical instrument classification using non-negative matrix
  factorization algorithms and subset feature selection}.
In: \bbtitle{Proceedings of the IEEE International Conference on Acoustics,
  Speech, and Signal Processing (ICASSP)}
(\byear{2006})
\end{bchapter}
\endbibitem

%%% 30
\bibitem{bhalke2016jiis}
\begin{barticle}
\bauthor{\bsnm{Bhalke}, \binits{D.G.}},
\bauthor{\bsnm{Rao}, \binits{C.B.R.}},
\bauthor{\bsnm{Bormane}, \binits{D.S.}}:
\batitle{{Automatic musical instrument classification using fractional Fourier
  transform based-MFCC features and counter propagation neural network}}.
\bjtitle{Journal of Intelligent Information Systems}
\bvolume{46}(\bissue{3}),
\bfpage{425}--\blpage{446}
(\byear{2016})
\end{barticle}
\endbibitem

%%% 31
\bibitem{humphrey2018ismir}
\begin{bchapter}
\bauthor{\bsnm{Humphrey}, \binits{E.}},
\bauthor{\bsnm{Durand}, \binits{S.}},
\bauthor{\bsnm{McFee}, \binits{B.}}:
\bctitle{Openmic-2018: an open dataset for multiple instrument recognition}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2018})
\end{bchapter}
\endbibitem

%%% 32
\bibitem{mcfee2016ismir}
\begin{bchapter}
\bauthor{\bsnm{McFee}, \binits{B.}},
\bauthor{\bsnm{Humphrey}, \binits{E.J.}},
\bauthor{\bsnm{Urbano}, \binits{J.}}:
\bctitle{{A plan for sustainable {MIR} evaluation}}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2016})
\end{bchapter}
\endbibitem

%%% 33
\bibitem{defferrard2017ismir}
\begin{bchapter}
\bauthor{\bsnm{Defferrard}, \binits{M.}},
\bauthor{\bsnm{Benzi}, \binits{K.}},
\bauthor{\bsnm{Vandergheynst}, \binits{P.}},
\bauthor{\bsnm{Bresson}, \binits{X.}}:
\bctitle{{FMA: A dataset for music analysis}}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2017})
\end{bchapter}
\endbibitem

%%% 34
\bibitem{lostanlen2016ismir}
\begin{bchapter}
\bauthor{\bsnm{Lostanlen}, \binits{V.}},
\bauthor{\bsnm{Cella}, \binits{C.E.}}:
\bctitle{Deep convolutional networks on the pitch spiral for musical instrument
  recognition}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2016})
\end{bchapter}
\endbibitem

%%% 35
\bibitem{bittner2014ismir}
\begin{bchapter}
\bauthor{\bsnm{Bittner}, \binits{R.M.}},
\bauthor{\bsnm{Salamon}, \binits{J.}},
\bauthor{\bsnm{Tierney}, \binits{M.}},
\bauthor{\bsnm{Mauch}, \binits{M.}},
\bauthor{\bsnm{Cannam}, \binits{C.}},
\bauthor{\bsnm{Bello}, \binits{J.P.}}:
\bctitle{{MedleyDB: A multitrack dataset for annotation-intensive MIR
  research}}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2014})
\end{bchapter}
\endbibitem

%%% 36
\bibitem{mcfee2015ismir}
\begin{bchapter}
\bauthor{\bsnm{McFee}, \binits{B.}},
\bauthor{\bsnm{Humphrey}, \binits{E.}},
\bauthor{\bsnm{Bello}, \binits{J.}}:
\bctitle{A software framework for musical data augmentation}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR)}
(\byear{2015})
\end{bchapter}
\endbibitem

%%% 37
\bibitem{pons2017eusipco}
\begin{bchapter}
\bauthor{\bsnm{{Pons}}, \binits{J.}},
\bauthor{\bsnm{{Slizovskaia}}, \binits{O.}},
\bauthor{\bsnm{{Gong}}, \binits{R.}},
\bauthor{\bsnm{{G\'{o}mez}}, \binits{E.}},
\bauthor{\bsnm{{Serra}}, \binits{X.}}:
\bctitle{Timbre analysis of music audio signals with convolutional neural
  networks}.
In: \bbtitle{25th European Signal Processing Conference (EUSIPCO)},
pp. \bfpage{2744}--\blpage{2748}
(\byear{2017})
\end{bchapter}
\endbibitem

%%% 38
\bibitem{gururani2018ismir}
\begin{bchapter}
\bauthor{\bsnm{Gururani}, \binits{S.}},
\bauthor{\bsnm{Summers}, \binits{C.}},
\bauthor{\bsnm{Lerch}, \binits{A.}}:
\bctitle{Instrument activity detection in polyphonic music using deep neural
  networks.}
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2018})
\end{bchapter}
\endbibitem

%%% 39
\bibitem{loureiro2004ismir}
\begin{bchapter}
\bauthor{\bsnm{Loureiro}, \binits{M.A.}},
\bauthor{\bparticle{de} \bsnm{Paula}, \binits{H.B.}},
\bauthor{\bsnm{Yehia}, \binits{H.C.}}:
\bctitle{Timbre classification of a single musical instrument}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference}
(\byear{2004})
\end{bchapter}
\endbibitem

%%% 40
\bibitem{han2017taslp}
\begin{barticle}
\bauthor{\bsnm{Han}, \binits{Y.}},
\bauthor{\bsnm{Kim}, \binits{J.}},
\bauthor{\bsnm{Lee}, \binits{K.}}:
\batitle{Deep convolutional neural networks for predominant instrument
  recognition in polyphonic music}.
\bjtitle{IEEE Transactions on Audio, Speech, and Language Processing}
\bvolume{25}(\bissue{1}),
\bfpage{208}--\blpage{221}
(\byear{2017})
\end{barticle}
\endbibitem

%%% 41
\bibitem{mcadams2009chapter}
\begin{bbook}
\bauthor{\bsnm{McAdams}, \binits{S.}},
\bauthor{\bsnm{Giordano}, \binits{B.L.}}:
\bbtitle{The perception of musical timbre},
pp. \bfpage{72}--\blpage{80}
(\byear{2009})
\end{bbook}
\endbibitem

%%% 42
\bibitem{depireux2001jneur}
\begin{barticle}
\bauthor{\bsnm{Depireux}, \binits{D.}},
\bauthor{\bsnm{Simon}, \binits{J.}},
\bauthor{\bsnm{Klein}, \binits{D.}},
\bauthor{\bsnm{Shamma}, \binits{S.}}:
\batitle{Spectro-temporal response field characterization with dynamic ripples
  in ferret primary auditory cortex}.
\bjtitle{Journal of Neurophysiology}
\bvolume{85}(\bissue{3}),
\bfpage{1220}--\blpage{1234}
(\byear{2001})
\end{barticle}
\endbibitem

%%% 43
\bibitem{aertsen1981biolcyb}
\begin{barticle}
\bauthor{\bsnm{Aertsen}, \binits{A.}},
\bauthor{\bsnm{Johannesma}, \binits{P.}}:
\batitle{The spectro-temporal receptive field}.
\bjtitle{Biological Cybernetics}
\bvolume{42}(\bissue{2}),
\bfpage{133}--\blpage{143}
(\byear{1981})
\end{barticle}
\endbibitem

%%% 44
\bibitem{deboer1968biomed}
\begin{botherref}
\oauthor{\bsnm{De~Boer}, \binits{E.}},
\oauthor{\bsnm{Kuyper}, \binits{P.}}:
Triggered correlation.
IEEE Transactions on Biomedical Engineering
(3),
169--179
(1968)
\end{botherref}
\endbibitem

%%% 45
\bibitem{flandrin1998book}
\begin{bbook}
\bauthor{\bsnm{Flandrin}, \binits{P.}}:
\bbtitle{Time-frequency/time-scale Analysis}.
\bpublisher{Academic press}, \blocation{???}
(\byear{1998})
\end{bbook}
\endbibitem

%%% 46
\bibitem{eggermont1993hearing}
\begin{barticle}
\bauthor{\bsnm{Eggermont}, \binits{J.}}:
\batitle{Wiener and volterra analyses applied to the auditory system}.
\bjtitle{Hearing research}
\bvolume{66}(\bissue{2}),
\bfpage{177}--\blpage{201}
(\byear{1993})
\end{barticle}
\endbibitem

%%% 47
\bibitem{klein2000compneur}
\begin{barticle}
\bauthor{\bsnm{Klein}, \binits{D.}},
\bauthor{\bsnm{Depireux}, \binits{D.}},
\bauthor{\bsnm{Simon}, \binits{J.}},
\bauthor{\bsnm{Shamma}, \binits{S.}}:
\batitle{Robust spectrotemporal reverse correlation for the auditory system:
  optimizing stimulus design}.
\bjtitle{Journal of Computational Neuroscience}
\bvolume{9}(\bissue{1}),
\bfpage{85}--\blpage{111}
(\byear{2000})
\end{barticle}
\endbibitem

%%% 48
\bibitem{theunissen2000jneur}
\begin{barticle}
\bauthor{\bsnm{Theunissen}, \binits{F.E.}},
\bauthor{\bsnm{Sen}, \binits{K.}},
\bauthor{\bsnm{Doupe}, \binits{A.J.}}:
\batitle{Spectral-temporal receptive fields of nonlinear auditory neurons
  obtained using natural sounds}.
\bjtitle{Journal of Neuroscience}
\bvolume{20}(\bissue{6}),
\bfpage{2315}--\blpage{2331}
(\byear{2000})
\end{barticle}
\endbibitem

%%% 49
\bibitem{chi2005jasa}
\begin{barticle}
\bauthor{\bsnm{Chi}, \binits{T.}},
\bauthor{\bsnm{Ru}, \binits{P.}},
\bauthor{\bsnm{Shamma}, \binits{S.A.}}:
\batitle{Multiresolution spectrotemporal analysis of complex sounds}.
\bjtitle{The Journal of the Acoustical Society of America}
\bvolume{118}(\bissue{2}),
\bfpage{887}--\blpage{906}
(\byear{2005})
\end{barticle}
\endbibitem

%%% 50
\bibitem{patil2015eurasip}
\begin{barticle}
\bauthor{\bsnm{Patil}, \binits{K.}},
\bauthor{\bsnm{Elhilali}, \binits{M.}}:
\batitle{Biomimetic spectro-temporal features for music instrument recognition
  in isolated notes and solo phrases}.
\bjtitle{EURASIP J. Audio Speech Music Process.}
\bvolume{2015}(\bissue{1}),
\bfpage{27}
(\byear{2015})
\end{barticle}
\endbibitem

%%% 51
\bibitem{thoret2016jasa}
\begin{barticle}
\bauthor{\bsnm{Thoret}, \binits{E.}},
\bauthor{\bsnm{Depalle}, \binits{P.}},
\bauthor{\bsnm{McAdams}, \binits{S.}}:
\batitle{Perceptually salient spectrotemporal modulations for recognition of
  sustained musical instruments}.
\bjtitle{The Journal of the Acoustical Society of America}
\bvolume{140}(\bissue{6}),
\bfpage{478}--\blpage{483}
(\byear{2016})
\end{barticle}
\endbibitem

%%% 52
\bibitem{mishra2018ismir}
\begin{bchapter}
\bauthor{\bsnm{Mishra}, \binits{S.}},
\bauthor{\bsnm{Sturm}, \binits{B.L.}},
\bauthor{\bsnm{Dixon}, \binits{S.}}:
\bctitle{Understanding a deep machine listening model through feature
  inversion}.
In: \bbtitle{Proceedings of the International Society on Music Information
  Retrieval (ISMIR) Conference},
pp. \bfpage{755}--\blpage{762}
(\byear{2018})
\end{bchapter}
\endbibitem

%%% 53
\bibitem{hemery2015frontiers}
\begin{botherref}
\oauthor{\bsnm{Hemery}, \binits{E.}},
\oauthor{\bsnm{Aucouturier}, \binits{J.}}:
One hundred ways to process time, frequency, rate and scale in the central
  auditory system: a pattern-recognition meta-analysis.
Frontiers in computational neuroscience
\textbf{9}
(2015)
\end{botherref}
\endbibitem

%%% 54
\bibitem{andreux2020jmlr}
\begin{botherref}
\oauthor{\bsnm{Andreux}, \binits{M.}},
\oauthor{\bsnm{Angles}, \binits{T.}},
\oauthor{\bsnm{Exarchakis}, \binits{G.}},
\oauthor{\bsnm{Leonarduzzi}, \binits{R.}},
\oauthor{\bsnm{Rochette}, \binits{G.}},
\oauthor{\bsnm{Thiry}, \binits{L.}},
\oauthor{\bsnm{Zarka}, \binits{J.}},
\oauthor{\bsnm{Mallat}, \binits{S.}},
\oauthor{\bsnm{Belilovsky}, \binits{E.}},
\oauthor{\bsnm{Bruna}, \binits{J.}}, et al.:
Kymatio: Scattering transforms in python.
Journal of Machine Learning Research
\textbf{21}(60)
(2020)
\end{botherref}
\endbibitem

%%% 55
\bibitem{lostanlen2019dafx}
\begin{bchapter}
\bauthor{\bsnm{Lostanlen}, \binits{V.}},
\bauthor{\bsnm{Hecker}, \binits{F.}}:
\bctitle{The shape of remixxxes to come: Audio texture synthesis with
  time--frequency scattering}.
In: \bbtitle{Proceedings of the Digital Audio Effects Conference (DAFX)}
(\byear{2019})
\end{bchapter}
\endbibitem

%%% 56
\bibitem{mallat2016philtrans}
\begin{barticle}
\bauthor{\bsnm{Mallat}, \binits{S.}}:
\batitle{Understanding deep convolutional networks}.
\bjtitle{Philosophical Transactions of the Royal Society A: Mathematical,
  Physical and Engineering Sciences}
\bvolume{374}(\bissue{2065}),
\bfpage{20150203}
(\byear{2016})
\end{barticle}
\endbibitem

%%% 57
\bibitem{wu2018taslp}
\begin{barticle}
\bauthor{\bsnm{Wu}, \binits{C.-W.}},
\bauthor{\bsnm{Dittmar}, \binits{C.}},
\bauthor{\bsnm{Southall}, \binits{C.}},
\bauthor{\bsnm{Vogl}, \binits{R.}},
\bauthor{\bsnm{Widmer}, \binits{G.}},
\bauthor{\bsnm{Hockman}, \binits{J.}},
\bauthor{\bsnm{Muller}, \binits{M.}},
\bauthor{\bsnm{Lerch}, \binits{A.}}:
\batitle{A review of automatic drum transcription}.
\bjtitle{IEEE Transactions on Audio, Speech, and Language Processing}
\bvolume{26}(\bissue{9}),
\bfpage{1457}--\blpage{1483}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 58
\bibitem{pearce2019appliedsciences}
\begin{barticle}
\bauthor{\bsnm{Pearce}, \binits{A.}},
\bauthor{\bsnm{Brookes}, \binits{T.}},
\bauthor{\bsnm{Mason}, \binits{R.}}:
\batitle{Modelling timbral hardness}.
\bjtitle{Applied Sciences}
\bvolume{9}(\bissue{3}),
\bfpage{466}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 59
\bibitem{kernighan1970efficient}
\begin{barticle}
\bauthor{\bsnm{Kernighan}, \binits{B.W.}},
\bauthor{\bsnm{Lin}, \binits{S.}}:
\batitle{An efficient heuristic procedure for partitioning graphs}.
\bjtitle{The Bell system technical journal}
\bvolume{49}(\bissue{2}),
\bfpage{291}--\blpage{307}
(\byear{1970})
\end{barticle}
\endbibitem

%%% 60
\bibitem{han1997scalable}
\begin{bbook}
\bauthor{\bsnm{Han}, \binits{E.-H.}},
\bauthor{\bsnm{Karypis}, \binits{G.}},
\bauthor{\bsnm{Kumar}, \binits{V.}}:
\bbtitle{Scalable Parallel Data Mining for Association Rules}
vol. \bseriesno{26}.
\bpublisher{ACM}, \blocation{???}
(\byear{1997})
\end{bbook}
\endbibitem

%%% 61
\bibitem{strehl2002cluster}
\begin{barticle}
\bauthor{\bsnm{Strehl}, \binits{A.}},
\bauthor{\bsnm{Ghosh}, \binits{J.}}:
\batitle{Cluster ensembles---a knowledge reuse framework for combining multiple
  partitions}.
\bjtitle{Journal of machine learning research}
\bvolume{3}(\bissue{Dec}),
\bfpage{583}--\blpage{617}
(\byear{2002})
\end{barticle}
\endbibitem

%%% 62
\bibitem{ward1963jasa}
\begin{barticle}
\bauthor{\bsnm{Ward~Jr.}, \binits{J.H.}}:
\batitle{Hierarchical grouping to optimize an objective function}.
\bjtitle{Journal of the American Statistical Association}
\bvolume{58}(\bissue{301}),
\bfpage{236}--\blpage{244}
(\byear{1963})
\end{barticle}
\endbibitem
